---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# twopointzerothree

<!-- badges: start -->
<!-- badges: end -->

`twopointzerothree` is motivated by an [expression of concern](https://pubpeer.com/publications/BF638A197BC80D145674D8118BE37F) concerning a paper coauthored by Dr Pruitt following the discovery, amongst other issues, that 

> Seven consecutive values from _Theridon_ agressiveness assay #1 differ exactly by + 2.03 from another exact sequence in aggressiveness assay #1 in a different treatment group

I wanted to know how this could be done. 
As far as I know, standard tools (n-grams) only detect duplicate sequences, not duplicate sequences with an offset.

`twopointzerothree` develops a method for detecting duplicate offset sequences by searching for repeat sequences of perfectly correlated numbers.
These repeat sequences are either duplicates or offset duplicates.

`twopointzerothree` can be installed with 

```{r install, eval = FALSE}
remotes::install_github("Sorbus-torminalis/twopointzerothree.git")
```

`twopointzerothree` requires a vector of numbers as input and the maximum length of duplicate to search for (`sequence_longest` can report the length of the longest). 

```{r example}
library(twopointzerothree)
data("kp2014")# part of the data from Keiser & Pruitt 2014
sequence_find(vec = kp2014$`Theridion murarium Aggressiveness...4`, max = 9)
```

The result give the position and values of the first and second sets of duplicated values and any offset.

If data in several columns need to be checked, they should be appended into one vector.

```{r example2}
sequence_find(
  vec = c(kp2014$`Theridion murarium Aggressiveness...4`,
          kp2014$`Theridion murarium Aggressiveness...5`,
          kp2014$`Theridion murarium Aggressiveness...6`),
  max = 9)
```

## Notes

`twopointzerothree` will report the longest sequence of duplicates sequences it can find that are at most `max` elements long.
To find shorter sequences, reduce `max`.
If `max` is less than the length of the longest sequence, it `sequence_find` will return overlapping sequences.

`twopointzerothree` will not report sequences of identical values as duplicates as `cor(rep(1, 3), rep(2, 3))` returns NA.

`twopointzerothree` reports duplicate values.
It does not report why. 

If you find this package useful or have ideas about how it could be improve, please leave a message in the issues tab.

