---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# twopointzerothree

<!-- badges: start -->
<!-- badges: end -->

twopointzerothree is motivated by an [expression of concern](https://pubpeer.com/publications/BF638A197BC80D145674D8118BE37F) concerning a paper coauthored by Dr Pruitt following the discovery, amongst other issues, that 

> Seven consecutive values from _Theridon_ agressiveness assay #1 differ exactly by + 2.03 from another exact sequence in aggressiveness assay #1 in a different treatment group

I wanted to know how this could be done. 
Standard tools (n-grams) only detect duplicate sequences not duplicate sequences with an offset.

twopointzerothree develops a method for detecting duplicate offset sequences.

It can be installed with 

```{r install, eval = FALSE}
remotes::install_github("Sorbus-torminalis/twopointzerothree.git")
```


